\documentclass[a5paper,10pt,twoside]{memoir}
\pagestyle{empty}
\renewcommand{\PoemTitlefont}{%
\normalfont\scshape\flushleft% Remove centering from poem title
\hspace*{0.5\linewidth}\hspace*{-0.5\versewidth}}% Makes poem title flush left with body block.

\checkandfixthelayout

\begin{document}

\settowidth{\versewidth}{Because traveling is a tremendously stressful task of uneven worth}
\PlainPoemTitle % Removes the counter from \PoemTitle
\PoemTitle{The Trouble with Travel}
\begin{verse}[\versewidth]

To ride down the road, or the rails on a train\\
To get where I'm going. What grief. Oh, what pain\\
Is invoked in evaluation of vehicles to take\\
I can't make up my mind. Have mercy! Give me a break\\
What's important is the place where I'll probably end up\\
It's a land that I like with no lack of full cup\\
To get there is ghastly but go there, I must\\
I s'pose I could spin a display sign that says, "\_\_\_\_\_ or bust"\\
Would that generate some generosity or general goodwill\\
In a motorist that moves by me at that moment? I wonder still\\
It'd be perfect to be a pilot. I'd have a pass to bliss\\
I would fly there and be free, feeling far from remiss\\
Oh, but wait. It'd be worthless 'cuz without a plane\\
To be a pilot becomes pointless. Back to planning again\\
This is why I'm not willing to wander the earth\\
Because traveling is a tremendously stressful task of uneven worth\\
The grass appears greener when it grows in a different place\\
Guess I'll learn how to like my location, just in case\\
\end{verse}

\end{document}
